Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-04-08 man/figures/evi_vs_severe_droughts.Rmd
fix figure typo

```{r}
# PLOT EVI + DROUGHT 
combinado2 <- ggplot(evi_profile_dat, aes(cd, y=mean)) + 
  scale_x_date(labels = function(x) format(x, "%b"), breaks = date_breaks('month')) + 
  theme_bw() +
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank()) +
  theme_classic() +
  geom_segment(data = dy, aes(y = mean, x= iD, xend =eD, yend = mean, colour = d_severity), 
               size = 8, alpha = 0.7) +
  geom_text(data = dy, aes(label = year, x = (iD + floor(eD-iD)/2))) +
  scale_colour_gradient(low = "orange", high = "brown") + 
  labs(colour = "Drought Severity") +
  geom_errorbar(aes(ymin = mean - 10*se, ymax= mean + 10*se), width=4, colour=micolor, size=.8) + 
  geom_line(colour=micolor, size=.8) + 
  geom_point(size=3,colour=micolor) +
  geom_point(size=1.5, colour='white') + 
  ylab('EVI') + xlab('')

>>>>

```{r}
micolor <- '#455883'

# PLOT EVI + DROUGHT 
combinado2 <- ggplot(evi_profile_dat, aes(cd, y=mean)) + 
  scale_x_date(labels = function(x) format(x, "%b"), breaks = date_breaks('month')) + 
  theme_bw() +
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank()) +
  theme_classic() +
  geom_segment(data = dy, aes(y = mean, x= iD, xend =eD, yend = mean, colour = d_severity), 
               size = 8, alpha = 0.7) +
  geom_text(data = dy, aes(label = year, x = (iD + floor(eD-iD)/2))) +
  scale_colour_gradient(low = "orange", high = "brown") + 
  labs(colour = "Drought Severity") +
  geom_errorbar(aes(ymin = mean - 10*se, ymax= mean + 10*se), width=4, colour=micolor, size=.8) + 
  geom_line(colour=micolor, size=.8) + 
  geom_point(size=3,colour=micolor) +
  geom_point(size=1.5, colour='white') + 
  ylab('EVI') + xlab('')

### 2019-04-08 man/figures/resilience_long_term.Rmd
fix figure typo

  ggplot(df, aes_string(y=paste0(v, "_mean_mean"), x=x, label=label)) + 
    geom_smooth(method='lm', se=FALSE, colour="gray") +
    geom_errorbar(mapping = yerrbar) + 
    geom_point(size=1.5, pch = 21, colour="black", fill="white") + 
    theme_bw() + 
    geom_text_repel(nudge_x = 0.5, size = 3) + 
    annotate("text", x=coordX_eq, y = coordY_eq, 
             label=lm_eqn(lm(formulita, df)), parse=TRUE, 
             size = 4.5, fontface = "bold") +
    ggtitle(titulo) + 
    theme(plot.title = element_text(size = 11, face = "bold.italic"),
          panel.grid = element_blank(), 
          axis.text.y = element_text(size=9),
          axis.text.x = element_text(size=9),
          axis.title = element_text(size = 10))

@@

```{r plot_rt}
sevRt <- plotrel(sdf, v = "rt", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 10, coordY_eq = 0.5, titulo = "Rt") +
  xlab('') + ylab('') +
  theme(plot.margin = margin(r=-0.7, l=0, t=0, b=0, "pt"))

i <- summary(lm(rt_mean_mean~d_severity, data=sdf))
```

```{r plot_rs}
sevRs <- plotrel(sdf, v = "rs", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 10, coordY_eq = 0.5, titulo = "Rs") + 
  xlab('') + ylab('') +
  theme(plot.margin = margin(r=0, l=-0.7, t=0, b=0, "pt"))

summary(lm(rs_mean_mean~d_severity, data=sdf))
```

```{r plot_rc}
sevRc <- plotrel(sdf, v = "rc", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 10, coordY_eq = 0.5, titulo = "Rc") +
  xlab("Drought Severity") + ylab('') +
  theme(plot.margin = margin(r=-0.7, l=-0.7, t=0, b=0, "pt"))
```

>>>>

  ggplot(df, aes_string(y=paste0(v, "_mean_mean"), x=x, label=label)) + 
    geom_smooth(method='lm', se=FALSE, colour="gray") +
    geom_errorbar(mapping = yerrbar) + 
    geom_point(size=1.5, pch = 21, colour="black", fill="white") + 
    theme_bw() + 
    geom_text_repel(nudge_x = 0.5, size = 3) + 
    annotate("text", x = coordX_eq, y = coordY_eq, 
             label=lm_eqn(lm(formulita, df)), parse=TRUE, 
             size = 3, fontface = "bold", hjust="left") +
    ggtitle(titulo) + 
    theme(plot.title = element_text(size = 11, face = "bold.italic"),
          panel.grid = element_blank(), 
          axis.text.y = element_text(size=9),
          axis.text.x = element_text(size=9),
          axis.title = element_text(size = 10))

@@

```{r plot_rt}
sevRt <- plotrel(sdf, v = "rt", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 6, coordY_eq = 0.5, titulo = "Rt") +
  xlab('') + ylab('') +
  theme(plot.margin = margin(r=-0.7, l=0, t=0, b=0, "pt"))

```{r plot_rs}
sevRs <- plotrel(sdf, v = "rs", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 6, coordY_eq = 0.5, titulo = "Rs") + 
  xlab('') + ylab('') +
  theme(plot.margin = margin(r=0, l=-0.7, t=0, b=0, "pt"))
```

```{r plot_rc}
sevRc <- plotrel(sdf, v = "rc", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 6, coordY_eq = 0.5, titulo = "Rc") +
  xlab("Drought Severity") + ylab('') +
  theme(plot.margin = margin(r=-0.7, l=-0.7, t=0, b=0, "pt"))
```
